Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-06-04 paper/agujournaltemplate.tex
Update paper

The median of the tremor depth minus the plate model is 1.92 km for the McCrory model and 1.8 km for the Preston model, while the Qn estimator of scale for these models is 1.39 and 1.31 km. So, to a very good approximation,  the tremor appears to coincide with the plate boundary.

>>>>

The median of the absolute value of the difference between the depth of the plate boundary and the depth of the tremor is 1.92 km for the McCrory model and 1.88 km for the Preston model. The median of the difference between the depth of the plate boundary and the depth of the tremor is -0.85 km for the McCrory model, and -0.21 km for the Preston model, which locates the tremor at the plate boundary or a little bit above. The Qn estimator of scale for these models is 1.39 and 1.31 km. So, to a very good approximation,  the tremor appears to coincide with the plate boundary. \\

By comparison, Qn estimator of scale for the low-frequency earthquakes is 0.99 km for the McCrory model and 0.87 km for the Preston model. The median of the absolute value of the difference between the depth of the plate boundary and the depth of the LFEs is 1.22 km for the McCrory model and 0.96 km for the Preston model. The median of the difference between the depth of the plate boundary and the depth of the LFEs is -0.49 km for the McCrory model and -0.19 km for the Preston model, which locates the LFEs at the plate boundary or a little bit above.
